---
title: "New Edited Data EDA"
output: html_notebook
---

```{r}
rm(list=ls(all=TRUE))
```


```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(corrplot)
library(stargazer)
library(tidyr)
library(tidyverse)
library(ggplot2)
```

```{r}
raw_dat <- read.csv('Raw_Project_Data_2.csv')
```

```{r}
dummy_dat = data.frame(
  # citizenship
  born_citizen = if_else(raw_dat$CITIZENSHIP == 1, 1, if_else(raw_dat$CITIZENSHIP == 2, 1, if_else(raw_dat$CITIZENSHIP == 3, 1, 0))),
  naturalized_citizen = if_else(raw_dat$CITIZENSHIP == 4, 1, 0),
  not_citizen = if_else(raw_dat$CITIZENSHIP == 5, 1, 0),
  
  # worker classification
  INLF = if_else(raw_dat$WORKER_CLASS == 'b', 1, 0),
  private_sector = if_else(raw_dat$WORKER_CLASS == 1, 1, 0),
  gov_sector = if_else(raw_dat$WORKER_CLASS == 2, 1, if_else(raw_dat$WORKER_CLASS == 3, 1, if_else(raw_dat$WORKER_CLASS == 4, 1, if_else(raw_dat$WORKER_CLASS == 5, 1, 0)))),
  self_employed = if_else(raw_dat$WORKER_CLASS == 5, 1, if_else(raw_dat$WORKER_CLASS == 6, 1, 0)),
  without_pay = if_else(raw_dat$WORKER_CLASS == 8, 1, 0),
  unemployed = if_else(raw_dat$WORKER_CLASS == 9, 1, 0),
  
  # ability to speak english
  under5_english = if_else(raw_dat$ENGLISH_ABILITY == 'b', 1, 0),
  eng_very_well = if_else(raw_dat$ENGLISH_ABILITY == 1, 1, 0),
  eng_well = if_else(raw_dat$ENGLISH_ABILITY == 2, 1, 0),
  eng_not_well = if_else(raw_dat$ENGLISH_ABILITY == 3, 1, 0),
  eng_none = if_else(raw_dat$ENGLISH_ABILITY == 4, 1, 0),
  
  # bi-lingual
  under5_multi = if_else(raw_dat$OTHER_LANGUAGE == 'b', 1, 0),
  multilingual = if_else(raw_dat$OTHER_LANGUAGE == 1, 1, 0),
  
  # martial status
  married = if_else(raw_dat$MAR_STATUS == 1, 1, 0),
  widowed = if_else(raw_dat$MAR_STATUS == 2, 1, 0),
  divorced = if_else(raw_dat$MAR_STATUS == 3, 1, 0),
  separated = if_else(raw_dat$MAR_STATUS == 4, 1, 0),
  single = if_else(raw_dat$MAR_STATUS == 5, 1, 0),

  # educational obtainment
  under_5_edu = if_else(raw_dat$EDU_LEVEL == 'bb', 1, 0),
  uncomplete_edu = if_else(raw_dat$EDU_LEVEL == 01, 1, 0),
  primary_edu = if_else(raw_dat$EDU_LEVEL == 03, 1, if_else(raw_dat$EDU_LEVEL == 04, 1, if_else(raw_dat$EDU_LEVEL == 05, 1, if_else(raw_dat$EDU_LEVEL == 06, 1, if_else(raw_dat$EDU_LEVEL == 07, 1, if_else(raw_dat$EDU_LEVEL == 08, 1, if_else(raw_dat$EDU_LEVEL == 09, 1, if_else(raw_dat$EDU_LEVEL == 10, 1, if_else(raw_dat$EDU_LEVEL == 11, 1, 0))))))))),
  secondary_edu = if_else(raw_dat$EDU_LEVEL == 15, 1, 0),
  secondary_diploma = if_else(raw_dat$EDU_LEVEL == 16, 1, 0),
  secondary_complete = if_else(raw_dat$EDU_LEVEL == 15, 1, if_else(raw_dat$EDU_LEVEL == 16, 1, if_else(raw_dat$EDU_LEVEL == 17, 1, 0))),
  GED = if_else(raw_dat$EDU_LEVEL == 17, 1,0),
  some_secondary = if_else(raw_dat$EDU_LEVEL == 12, 1, if_else(raw_dat$EDU_LEVEL == 13, 1,if_else(raw_dat$EDU_LEVEL == 14, 1, if_else(raw_dat$EDU_LEVEL == 15, 1, 0)))),
  associates = if_else(raw_dat$EDU_LEVEL == 20, 1, 0),
  bachelors = if_else(raw_dat$EDU_LEVEL == 21, 1, 0),
  some_college = if_else(raw_dat$EDU_LEVEL == 18, 1, if_else(raw_dat$EDU_LEVEL == 19, 1, 0)),
  masters = if_else(raw_dat$EDU_LEVEL == 22, 1, 0),
  professional = if_else(raw_dat$EDU_LEVEL == 23, 1, 0),
  doctoral = if_else(raw_dat$EDU_LEVEL == 24, 1, 0),
  
  # sex
  male = if_else(raw_dat$SEX == 1, 1, 0),
  female = if_else(raw_dat$SEX == 2, 1, 0),
  
  # disability
  disability_dummy = if_else(raw_dat$DISABILITY == 1, 1, 0),
  
  # nativity
  nativity_dummy = if_else(raw_dat$NATIVITY == 1, 1, 0),
  
  # nativity of parents
  not_child = if_else(raw_dat$SECOND_GEN == 'b', 1, 0),
  not_second = if_else(raw_dat$SECOND_GEN == 1, 1, if_else(raw_dat$SECOND_GEN == 5, 1, if_else(raw_dat$SECOND_GEN == 7, 1, 0))),
  second_gen_dummy = if_else(raw_dat$SECOND_GEN == 2, 1, if_else(raw_dat$SECOND_GEN == 3, 1, if_else(raw_dat$SECOND_GEN == 4, 1, if_else(raw_dat$SECOND_GEN == 6, 1, if_else(raw_dat$SECOND_GEN == 8, 1, 0))))),
  
  # race
  
  white = if_else(raw_dat$RACE == 1, 1, 0),
  black_african = if_else(raw_dat$RACE == 2, 1, 0),
  native_indian = if_else(raw_dat$RACE == 3, 1, 0),
  alaskan_native = if_else(raw_dat$RACE == 4, 1, 0),
  native_american = if_else(raw_dat$RACE == 5, 1, 0),
  asian_alone = if_else(raw_dat$RACE == 6, 1, 0),
  hawaian_alone = if_else(raw_dat$RACE == 7, 1, 0),
  two_race = if_else(raw_dat$RACE == 8, 1, 0),
  mixed_race = if_else(raw_dat$RACE == 9, 1, 0),
  
  welfare = if_else(raw_dat$SUPP_INC > 0, 1, if_else(raw_dat$SOCIAL_SECURITY > 0, 1, 0))
)
```

```{r}
FIN_DAT <- dummy_dat
```

```{r}
FIN_DAT$SERIAL_NO <- raw_dat$SERIALNO
FIN_DAT$EARNINGS <- raw_dat$EARNINGS
FIN_DAT$INCOME <- raw_dat$INCOME
FIN_DAT$WAGE <- raw_dat$WAGE
FIN_DAT$AGE <- raw_dat$AGE
FIN_DAT$SUPP_INC <- raw_dat$SUPP_INC 
FIN_DAT$SOCIAL_SECURITY <- raw_dat$SOCIAL_SECURITY 
FIN_DAT$HR_WORKED <- raw_dat$HOURS_WORKED 
FIN_DAT$WK_WORKED <- raw_dat$WEEKS_WORKED 

```

```{r}
FIN_DAT$SERIAL_NO <- FIN_DAT$SERIAL_NO
FIN_DAT$EARNINGS <- FIN_DAT$EARNINGS
FIN_DAT$INCOME <- FIN_DAT$INCOME
FIN_DAT$WAGE <- FIN_DAT$WAGE
FIN_DAT$AGE <- FIN_DAT$AGE 
FIN_DAT$SUPP_INC <- FIN_DAT$SUPP_INC 
FIN_DAT$SOCIAL_SECURITY <- FIN_DAT$SOCIAL_SECURITY 
FIN_DAT$HR_WORKED <- FIN_DAT$HR_WORKED
FIN_DAT$WK_WORKED <- FIN_DAT$WK_WORKED 
FIN_DAT$B_CIT <- FIN_DAT$born_citizen 
FIN_DAT$NAT_CIT <- FIN_DAT$naturalized_citizen 
FIN_DAT$NOT_CIT <- FIN_DAT$not_citizen 
FIN_DAT$NOT_LB <- FIN_DAT$INLF 
FIN_DAT$PRI_SEC <- FIN_DAT$private_sector 
FIN_DAT$GOV_SEC <- FIN_DAT$gov_sector 
FIN_DAT$SELF_EMP <- FIN_DAT$self_employed 
FIN_DAT$WRK_UNPAID <- FIN_DAT$without_pay 
FIN_DAT$UNEMP <- FIN_DAT$unemployed 
FIN_DAT$UNDER_ENG <- FIN_DAT$under5_english 
FIN_DAT$ENG_VW <- FIN_DAT$ eng_very_well 
FIN_DAT$ENG_W <- FIN_DAT$eng_well 
FIN_DAT$ENG_NW <- FIN_DAT$eng_not_well 
FIN_DAT$ENG_NON <- FIN_DAT$eng_none 
FIN_DAT$UNDER_MULTI <- FIN_DAT$under5_multi 
FIN_DAT$MULTI <- FIN_DAT$ multilingual 
FIN_DAT$MARRIED <- FIN_DAT$ married 
FIN_DAT$WIDOWED <- FIN_DAT$widowed 
FIN_DAT$DIVORCED <- FIN_DAT$divorced 
FIN_DAT$SEPARATED <- FIN_DAT$separated 
FIN_DAT$NOT_MARRIED <- FIN_DAT$not_married 
FIN_DAT$SINGLE <- FIN_DAT$single
FIN_DAT$UNDER_EDU <- FIN_DAT$under_5_edu 
FIN_DAT$INCOMP_EDU <- FIN_DAT$uncomplete_edu 
FIN_DAT$PRIM_EDU <- FIN_DAT$primary_edu 
FIN_DAT$SEC_INCOMP <- FIN_DAT$secondary_edu 
FIN_DAT$SEC_DIP <- FIN_DAT$secondary_diploma 
FIN_DAT$SEC_EDU <- FIN_DAT$secondary_complete 
FIN_DAT$GED_EDU <- FIN_DAT$GED 
FIN_DAT$SOME_SEC <- FIN_DAT$some_secondary 
FIN_DAT$AST_EDU <- FIN_DAT$associates
FIN_DAT$BACH_EDU <- FIN_DAT$bachelors 
FIN_DAT$SOME_COL <- FIN_DAT$some_college 
FIN_DAT$MAST_EDU <- FIN_DAT$ masters 
FIN_DAT$PROF_EDU <- FIN_DAT$professional 
FIN_DAT$DOC_EDU <- FIN_DAT$doctoral 
FIN_DAT$MALE <- FIN_DAT$male 
FIN_DAT$FEMALE <- FIN_DAT$female 
FIN_DAT$DISABILITY <- FIN_DAT$disability_dummy 
FIN_DAT$NATIVITY <- FIN_DAT$nativity_dummy 
FIN_DAT$NOT_CHILD <- FIN_DAT$not_child 
FIN_DAT$NOT_SEC <- FIN_DAT$not_second 
FIN_DAT$SEC_GEN <- FIN_DAT$second_gen_dummy
FIN_DAT$WHITE <- FIN_DAT$white
FIN_DAT$BLK_AFRI <- FIN_DAT$black_african
FIN_DAT$NAT_AMR <- FIN_DAT$native_indian
FIN_DAT$ALASKAN <- FIN_DAT$alaskan_native
FIN_DAT$INDIGINEOUS <- FIN_DAT$native_american
FIN_DAT$ASIAN <- FIN_DAT$asian_alone
FIN_DAT$HAWAIAN <- FIN_DAT$hawaian_alone
FIN_DAT$BI_RACIAL <- FIN_DAT$two_race
FIN_DAT$MULTI_RACIAL <- FIN_DAT$mixed_race
FIN_DAT$WELFARE <- FIN_DAT$welfare
```

```{r}
NEW_DAT <- FIN_DAT
```

```{r}
NEW_DAT$INCOME <- NULL
NEW_DAT$WAGE <- NULL
NEW_DAT$HOURS_WORKED <- NULL 
NEW_DAT$WEEKS_WORKED <- NULL 
NEW_DAT$born_citizen <- NULL 
NEW_DAT$naturalized_citizen <- NULL 
NEW_DAT$not_citizen <- NULL 
NEW_DAT$INLF <- NULL 
NEW_DAT$private_sector <- NULL 
NEW_DAT$gov_sector <- NULL 
NEW_DAT$self_employed <- NULL 
NEW_DAT$without_pay <- NULL 
NEW_DAT$unemployed <- NULL 
NEW_DAT$under5_english <- NULL 
NEW_DAT$ eng_very_well <- NULL 
NEW_DAT$eng_well <- NULL 
NEW_DAT$eng_not_well <- NULL 
NEW_DAT$eng_none <- NULL 
NEW_DAT$under5_multi <- NULL 
NEW_DAT$multilingual <- NULL 
NEW_DAT$married <- NULL 
NEW_DAT$widowed <- NULL 
NEW_DAT$divorced <- NULL 
NEW_DAT$separated <- NULL 
NEW_DAT$not_married <- NULL 
NEW_DAT$single <- NULL
NEW_DAT$under_5_edu <- NULL 
NEW_DAT$uncomplete_edu <- NULL 
NEW_DAT$primary_edu <- NULL 
NEW_DAT$secondary_edu <- NULL 
NEW_DAT$secondary_diploma <- NULL 
NEW_DAT$secondary_complete <- NULL 
NEW_DAT$GED <- NULL 
NEW_DAT$some_secondary <- NULL 
NEW_DAT$associates <- NULL
NEW_DAT$bachelors <- NULL 
NEW_DAT$some_college <- NULL 
NEW_DAT$ masters <- NULL 
NEW_DAT$professional <- NULL 
NEW_DAT$doctoral <- NULL 
NEW_DAT$male <- NULL 
NEW_DAT$female <- NULL 
NEW_DAT$disability_dummy <- NULL 
NEW_DAT$nativity_dummy <- NULL 
NEW_DAT$not_child <- NULL 
NEW_DAT$not_second <- NULL 
NEW_DAT$second_gen_dummy <- NULL
NEW_DAT$white <- NULL
NEW_DAT$black_african <- NULL
NEW_DAT$native_indian <- NULL
NEW_DAT$alaskan_native <- NULL
NEW_DAT$native_american <- NULL
NEW_DAT$asian_alone <- NULL
NEW_DAT$hawaian_alone <- NULL
NEW_DAT$two_race <- NULL
NEW_DAT$mixed_race <- NULL
NEW_DAT$welfare <- NULL
```

### REMOVE SECOND GEN VARIABLE, OVER 118K NAs
### REMOVE ENGLISH ABILITY, ~ 90K NAs
### REMOVE UNEMP, NOT_LB ~ REMOVED BECAUSE DATASET IS LIMITED TO EMPLOYED
### REMOVING UNDER_EDU, UNDER MULTI ~ LIMITED TO EMPLOYED BECAUSE DATASET IS LIMITED TO EMPLOYED, MINORS UNDER 16 CANNOT LEGALLY BE EMPLOYED

```{r}
NEW_DAT$NOT_LB <- NULL 
NEW_DAT$UNEMP <- NULL
NEW_DAT$UNDER_ENG <- NULL
NEW_DAT$ENG_VW <- NULL
NEW_DAT$ENG_W <- NULL
NEW_DAT$ENG_NW <- NULL
NEW_DAT$ENG_NON <- NULL
NEW_DAT$UNDER_MULTI <- NULL
NEW_DAT$UNDER_EDU <- NULL
NEW_DAT$NOT_CHILD <- NULL
NEW_DAT$NOT_SEC <- NULL
NEW_DAT$SEC_GEN <- NULL
```

### IMPOSING LIMITING CRITERIA TO STUDY ONLY EMPLOYED AND ADULT SEGEMENT OF LABOR FORCE

```{r}
RAW_LIMITED <- subset(raw_dat, EARNINGS > 0 & EARNINGS < 463000 & AGE >= 18)

NEW_DAT <- subset(NEW_DAT, EARNINGS > 0 & EARNINGS < 463000 & AGE >= 18)

```

```{r}
gazer_raw <- raw_dat
gazer_lim <- RAW_LIMITED
gazer_new <- NEW_DAT
```

```{r}
gazer_raw$SERIALNO <- NULL
gazer_lim$SERIALNO <- NULL
gazer_new$SERIAL_NO <- NULL
```


```{r}
stargazer(gazer_raw, type = "text", title = "Raw Texas Data Statistical Summary", colnames = TRUE, mean.sd = TRUE, median = TRUE, min.max = TRUE)

stargazer(gazer_lim, type = "text", title = "Limited Texas Data Statistical Summary", colnames = TRUE, mean.sd = TRUE, median = TRUE, min.max = TRUE)

stargazer(gazer_new, type = "text", title = "New Texas Data Statistical Summary", colnames = TRUE, mean.sd = TRUE, median = TRUE, min.max = TRUE)

```

```{r}
attach(NEW_DAT)
```

```{r}
colnames(NEW_DAT)
colnames(RAW_LIMITED)
```


```{r}
qplot(EARNINGS,
      geom="histogram",
      binwidth = 10000,  
      main = "Histogram for EARNINGS", 
      xlab = "EARNINGS",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(EARNINGS,
  main = "EARNINGS",
  xlab = "Count",
  ylab = "EARNINGS",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(EARNINGS), 
     main="EARNINGS DISTRIBUTION")
polygon(density(EARNINGS), col="pink", border="blue")

plot(EARNINGS)


```

# --------------------NEW_DAT----------------
* AGE vs EARNINGS
```{r}
qplot(AGE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for Age", 
      xlab = "Age",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(AGE,
  main = "Age",
  xlab = "Count",
  ylab = "Age",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(AGE), 
     main="AGE DISTRIBUTION")
polygon(density(AGE), col="pink", border="blue")


plot(AGE, EARNINGS)
```

* 
```{R}
colnames(NEW_DAT)
```
* SUPP_INC vs EARNINGS
```{r}
qplot(SUPP_INC,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SUPP_INC", 
      xlab = "SUPP_INC",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(SUPP_INC,
  main = "SUPP_INC",
  xlab = "Count",
  ylab = "SUPP_INC",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(SUPP_INC), 
     main="SUPP_INC DISTRIBUTION")
polygon(density(SUPP_INC), col="pink", border="blue")


plot(SUPP_INC, EARNINGS)
```
* SOCIAL_SECURITY vs EARNINGS
```{r}
qplot(SOCIAL_SECURITY,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SOCIAL_SECURITY", 
      xlab = "SOCIAL_SECURITY",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(SOCIAL_SECURITY,
  main = "SOCIAL_SECURITY",
  xlab = "Count",
  ylab = "SOCIAL_SECURITY",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(SOCIAL_SECURITY), 
     main="SOCIAL_SECURITY DISTRIBUTION")
polygon(density(SOCIAL_SECURITY), col="pink", border="blue")


plot(SOCIAL_SECURITY, EARNINGS)
```

* HR_WORKED vs EARNINGS
```{r}
qplot(HR_WORKED,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for HR_WORKED", 
      xlab = "HR_WORKED",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(HR_WORKED,
  main = "HR_WORKED",
  xlab = "Count",
  ylab = "HR_WORKED",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(HR_WORKED), 
     main="HR_WORKED DISTRIBUTION")
polygon(density(HR_WORKED), col="pink", border="blue")


plot(HR_WORKED, EARNINGS)
```
* WK_WORKED vs EARNINGS
```{r}
qplot(WK_WORKED,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for WK_WORKED", 
      xlab = "WK_WORKED",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(WK_WORKED,
  main = "WK_WORKED",
  xlab = "Count",
  ylab = "WK_WORKED",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(WK_WORKED), 
     main="WK_WORKED DISTRIBUTION")
polygon(density(WK_WORKED), col="pink", border="blue")


plot(WK_WORKED, EARNINGS)
```
* B_CIT vs EARNINGS
```{r}
qplot(B_CIT,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for B_CIT", 
      xlab = "B_CIT",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(B_CIT,
  main = "B_CIT",
  xlab = "Count",
  ylab = "B_CIT",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(B_CIT), 
     main="B_CIT DISTRIBUTION")
polygon(density(B_CIT), col="pink", border="blue")


plot(B_CIT, EARNINGS)
```
* NAT_CIT vs EARNINGS
```{r}
qplot(NAT_CIT,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for NAT_CIT", 
      xlab = "NAT_CIT",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(NAT_CIT,
  main = "NAT_CIT",
  xlab = "Count",
  ylab = "NAT_CIT",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(NAT_CIT), 
     main="NAT_CIT DISTRIBUTION")
polygon(density(NAT_CIT), col="pink", border="blue")


plot(NAT_CIT, EARNINGS)
```

* NOT_CIT vs EARNINGS

```{r}
qplot(NOT_CIT,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for NOT_CIT", 
      xlab = "NOT_CIT",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(NOT_CIT,
  main = "NOT_CIT",
  xlab = "Count",
  ylab = "NOT_CIT",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(NOT_CIT), 
     main="NOT_CIT DISTRIBUTION")
polygon(density(NOT_CIT), col="pink", border="blue")


plot(NOT_CIT, EARNINGS)
```

* PRI_SEC

```{r}
qplot(PRI_SEC,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for PRI_SEC", 
      xlab = "PRI_SEC",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(PRI_SEC,
  main = "PRI_SEC",
  xlab = "Count",
  ylab = "PRI_SEC",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(PRI_SEC), 
     main="PRI_SEC DISTRIBUTION")
polygon(density(PRI_SEC), col="pink", border="blue")


plot(PRI_SEC, EARNINGS)
```

* GOV_SEC
```{r}
qplot(GOV_SEC,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for GOV_SEC", 
      xlab = "GOV_SEC",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(GOV_SEC,
  main = "GOV_SEC",
  xlab = "Count",
  ylab = "GOV_SEC",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(GOV_SEC), 
     main="GOV_SEC DISTRIBUTION")
polygon(density(GOV_SEC), col="pink", border="blue")


plot(GOV_SEC, EARNINGS)
```
* SELF_EMP
```{r}
qplot(SELF_EMP,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SELF_EMP", 
      xlab = "SELF_EMP",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(SELF_EMP,
  main = "SELF_EMP",
  xlab = "Count",
  ylab = "SELF_EMP",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(SELF_EMP), 
     main="SELF_EMP DISTRIBUTION")
polygon(density(SELF_EMP), col="pink", border="blue")


plot(SELF_EMP, EARNINGS)
```

* WRK_UNPAID
```{r}
qplot(WRK_UNPAID,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for WRK_UNPAID", 
      xlab = "WRK_UNPAID",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(WRK_UNPAID,
  main = "WRK_UNPAID",
  xlab = "Count",
  ylab = "WRK_UNPAID",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(WRK_UNPAID), 
     main="WRK_UNPAID DISTRIBUTION")
polygon(density(WRK_UNPAID), col="pink", border="blue")


plot(WRK_UNPAID, EARNINGS)
```
* MULTI
```{r}
qplot(MULTI,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for MULTI", 
      xlab = "MULTI",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(MULTI,
  main = "MULTI",
  xlab = "Count",
  ylab = "MULTI",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(MULTI), 
     main="MULTI DISTRIBUTION")
polygon(density(MULTI), col="pink", border="blue")


plot(MULTI, EARNINGS)
```

* MARRIED
```{r}
qplot(MARRIED,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for MARRIED", 
      xlab = "MARRIED",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(MARRIED,
  main = "MARRIED",
  xlab = "Count",
  ylab = "MARRIED",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(MARRIED), 
     main="MARRIED DISTRIBUTION")
polygon(density(MARRIED), col="pink", border="blue")


plot(MARRIED, EARNINGS)
```

* WIDOWED
```{r}
qplot(WIDOWED,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for WIDOWED", 
      xlab = "WIDOWED",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(WIDOWED,
  main = "WIDOWED",
  xlab = "Count",
  ylab = "WIDOWED",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(WIDOWED), 
     main="WIDOWED DISTRIBUTION")
polygon(density(WIDOWED), col="pink", border="blue")


plot(WIDOWED, EARNINGS)
```
* DIVORCED

```{r}
qplot(DIVORCED,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for DIVORCED", 
      xlab = "DIVORCED",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(DIVORCED,
  main = "DIVORCED",
  xlab = "Count",
  ylab = "DIVORCED",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(DIVORCED), 
     main="DIVORCED DISTRIBUTION")
polygon(density(DIVORCED), col="pink", border="blue")


plot(DIVORCED, EARNINGS)
```
* SEPARATED

```{r}
qplot(SEPARATED,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SEPARATED", 
      xlab = "SEPARATED",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(SEPARATED,
  main = "SEPARATED",
  xlab = "Count",
  ylab = "SEPARATED",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(SEPARATED), 
     main="SEPARATED DISTRIBUTION")
polygon(density(SEPARATED), col="pink", border="blue")


plot(SEPARATED, EARNINGS)
```


* SINGLE

```{r}
qplot(SINGLE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SINGLE", 
      xlab = "SINGLE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(SINGLE,
  main = "SINGLE",
  xlab = "Count",
  ylab = "SINGLE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(SINGLE), 
     main="SINGLE DISTRIBUTION")
polygon(density(SINGLE), col="pink", border="blue")


plot(SINGLE, EARNINGS)
```

* INCOMP_EDU
```{r}
qplot(INCOMP_EDU,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for INCOMP_EDU", 
      xlab = "INCOMP_EDU",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(INCOMP_EDU,
  main = "INCOMP_EDU",
  xlab = "Count",
  ylab = "INCOMP_EDU",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(INCOMP_EDU), 
     main="INCOMP_EDU DISTRIBUTION")
polygon(density(INCOMP_EDU), col="pink", border="blue")


plot(INCOMP_EDU, EARNINGS)
```

* PRIM_EDU

```{r}
qplot(PRIM_EDU,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for PRIM_EDU", 
      xlab = "PRIM_EDU",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(PRIM_EDU,
  main = "PRIM_EDU",
  xlab = "Count",
  ylab = "PRIM_EDU",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(PRIM_EDU), 
     main="PRIM_EDU DISTRIBUTION")
polygon(density(PRIM_EDU), col="pink", border="blue")


plot(PRIM_EDU, EARNINGS)
```

* SEC_INCOMP
```{r}
qplot(SEC_INCOMP,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SEC_INCOMP", 
      xlab = "SEC_INCOMP",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(SEC_INCOMP,
  main = "SEC_INCOMP",
  xlab = "Count",
  ylab = "SEC_INCOMP",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(SEC_INCOMP), 
     main="SEC_INCOMP DISTRIBUTION")
polygon(density(SEC_INCOMP), col="pink", border="blue")


plot(SEC_INCOMP, EARNINGS)
```


* SEC_DIP
```{r}
qplot(SEC_DIP,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SEC_DIP", 
      xlab = "SEC_DIP",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(SEC_DIP,
  main = "SEC_DIP",
  xlab = "Count",
  ylab = "SEC_DIP",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(SEC_DIP), 
     main="SEC_DIP DISTRIBUTION")
polygon(density(SEC_DIP), col="pink", border="blue")


plot(SEC_DIP, EARNINGS)
```

* SEC_EDU
```{r}
qplot(SEC_EDU,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SEC_EDU", 
      xlab = "SEC_EDU",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(SEC_EDU,
  main = "SEC_EDU",
  xlab = "Count",
  ylab = "SEC_EDU",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(SEC_EDU), 
     main="SEC_EDU DISTRIBUTION")
polygon(density(SEC_EDU), col="pink", border="blue")


plot(SEC_EDU, EARNINGS)
```

* GED_EDU
```{r}
qplot(GED_EDU,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for GED_EDU", 
      xlab = "GED_EDU",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(GED_EDU,
  main = "GED_EDU",
  xlab = "Count",
  ylab = "GED_EDU",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(GED_EDU), 
     main="GED_EDU DISTRIBUTION")
polygon(density(GED_EDU), col="pink", border="blue")


plot(GED_EDU, EARNINGS)
```

* SOME_SEC
```{r}
qplot(SOME_SEC,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SOME_SEC", 
      xlab = "SOME_SEC",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(SOME_SEC,
  main = "SOME_SEC",
  xlab = "Count",
  ylab = "SOME_SEC",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(SOME_SEC), 
     main="SOME_SEC DISTRIBUTION")
polygon(density(SOME_SEC), col="pink", border="blue")


plot(SOME_SEC, EARNINGS)
```

* AST_EDU
```{r}
qplot(AST_EDU,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for AST_EDU", 
      xlab = "AST_EDU",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(AST_EDU,
  main = "AST_EDU",
  xlab = "Count",
  ylab = "AST_EDU",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(AST_EDU), 
     main="AST_EDU DISTRIBUTION")
polygon(density(AST_EDU), col="pink", border="blue")


plot(AST_EDU, EARNINGS)
```

* BACH_EDU
```{r}
qplot(BACH_EDU,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for BACH_EDU", 
      xlab = "BACH_EDU",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(BACH_EDU,
  main = "BACH_EDU",
  xlab = "Count",
  ylab = "BACH_EDU",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(BACH_EDU), 
     main="BACH_EDU DISTRIBUTION")
polygon(density(BACH_EDU), col="pink", border="blue")


plot(BACH_EDU, EARNINGS)
```
* SOME_COL
```{r}
qplot(SOME_COL,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SOME_COL", 
      xlab = "SOME_COL",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(SOME_COL,
  main = "SOME_COL",
  xlab = "Count",
  ylab = "SOME_COL",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(SOME_COL), 
     main="SOME_COL DISTRIBUTION")
polygon(density(SOME_COL), col="pink", border="blue")


plot(SOME_COL, EARNINGS)
```
* MAST_EDU

```{r}
qplot(MAST_EDU,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for MAST_EDU", 
      xlab = "MAST_EDU",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(MAST_EDU,
  main = "MAST_EDU",
  xlab = "Count",
  ylab = "MAST_EDU",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(MAST_EDU), 
     main="MAST_EDU DISTRIBUTION")
polygon(density(MAST_EDU), col="pink", border="blue")


plot(MAST_EDU, EARNINGS)
```

* PROF_EDU
```{r}
qplot(PROF_EDU,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for PROF_EDU", 
      xlab = "PROF_EDU",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(PROF_EDU,
  main = "PROF_EDU",
  xlab = "Count",
  ylab = "PROF_EDU",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(PROF_EDU), 
     main="PROF_EDU DISTRIBUTION")
polygon(density(PROF_EDU), col="pink", border="blue")


plot(PROF_EDU, EARNINGS)
```

* DOC_EDU
```{r}
qplot(DOC_EDU,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for DOC_EDU", 
      xlab = "DOC_EDU",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(DOC_EDU,
  main = "DOC_EDU",
  xlab = "Count",
  ylab = "DOC_EDU",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(DOC_EDU), 
     main="DOC_EDU DISTRIBUTION")
polygon(density(DOC_EDU), col="pink", border="blue")


plot(DOC_EDU, EARNINGS)
```

* DOC_EDU
```{r}
qplot(DOC_EDU,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for DOC_EDU", 
      xlab = "DOC_EDU",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(DOC_EDU,
  main = "DOC_EDU",
  xlab = "Count",
  ylab = "DOC_EDU",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(DOC_EDU), 
     main="DOC_EDU DISTRIBUTION")
polygon(density(DOC_EDU), col="pink", border="blue")


plot(DOC_EDU, EARNINGS)
```

* MALE
```{r}
qplot(MALE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for MALE", 
      xlab = "MALE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(MALE,
  main = "MALE",
  xlab = "Count",
  ylab = "MALE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(MALE), 
     main="MALE DISTRIBUTION")
polygon(density(MALE), col="pink", border="blue")


plot(MALE, EARNINGS)
```

* FEMALE
```{r}
qplot(FEMALE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for FEMALE", 
      xlab = "FEMALE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(FEMALE,
  main = "FEMALE",
  xlab = "Count",
  ylab = "FEMALE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(FEMALE), 
     main="DOC_EDU DISTRIBUTION")
polygon(density(FEMALE), col="pink", border="blue")


plot(FEMALE, EARNINGS)
```

* DISABILITY
```{r}
qplot(DISABILITY,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for DISABILITY", 
      xlab = "DISABILITY",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(DISABILITY,
  main = "DISABILITY",
  xlab = "Count",
  ylab = "DISABILITY",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(DISABILITY), 
     main="DISABILITY DISTRIBUTION")
polygon(density(DISABILITY), col="pink", border="blue")


plot(DISABILITY, EARNINGS)
```

* NATIVITY
```{r}
qplot(NATIVITY,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for NATIVITY", 
      xlab = "NATIVITY",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(NATIVITY,
  main = "NATIVITY",
  xlab = "Count",
  ylab = "NATIVITY",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(NATIVITY), 
     main="NATIVITY DISTRIBUTION")
polygon(density(NATIVITY), col="pink", border="blue")


plot(NATIVITY, EARNINGS)
```

* WHITE
```{r}
qplot(WHITE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for WHITE", 
      xlab = "WHITE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(WHITE,
  main = "WHITE",
  xlab = "Count",
  ylab = "WHITE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(WHITE), 
     main="WHITE DISTRIBUTION")
polygon(density(WHITE), col="pink", border="blue")


plot(WHITE, EARNINGS)
```

* BLK_AFRI
```{r}
qplot(BLK_AFRI,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for BLK_AFRI", 
      xlab = "BLK_AFRI",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(BLK_AFRI,
  main = "BLK_AFRI",
  xlab = "Count",
  ylab = "BLK_AFRI",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(BLK_AFRI), 
     main="BLK_AFRI DISTRIBUTION")
polygon(density(BLK_AFRI), col="pink", border="blue")


plot(BLK_AFRI, EARNINGS)
```

* NAT_AMR
```{r}
qplot(NAT_AMR,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for NAT_AMR", 
      xlab = "NAT_AMR",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(NAT_AMR,
  main = "NAT_AMR",
  xlab = "Count",
  ylab = "NAT_AMR",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(NAT_AMR), 
     main="NAT_AMR DISTRIBUTION")
polygon(density(NAT_AMR), col="pink", border="blue")


plot(NAT_AMR, EARNINGS)
```

* ALASKAN
```{r}
qplot(ALASKAN,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for ALASKAN", 
      xlab = "ALASKAN",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(ALASKAN,
  main = "ALASKAN",
  xlab = "Count",
  ylab = "ALASKAN",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(ALASKAN), 
     main="ALASKAN DISTRIBUTION")
polygon(density(ALASKAN), col="pink", border="blue")


plot(ALASKAN, EARNINGS)
```

* INDIGINEOUS
```{r}
qplot(INDIGINEOUS,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for INDIGINEOUS", 
      xlab = "INDIGINEOUS",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(INDIGINEOUS,
  main = "INDIGINEOUS",
  xlab = "Count",
  ylab = "INDIGINEOUS",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(INDIGINEOUS), 
     main="INDIGINEOUS DISTRIBUTION")
polygon(density(INDIGINEOUS), col="pink", border="blue")


plot(INDIGINEOUS, EARNINGS)
```

* ASIAN
```{r}
qplot(ASIAN,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for ASIAN", 
      xlab = "ASIAN",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(ASIAN,
  main = "ASIAN",
  xlab = "Count",
  ylab = "ASIAN",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(ASIAN), 
     main="ASIAN DISTRIBUTION")
polygon(density(ASIAN), col="pink", border="blue")


plot(ASIAN, EARNINGS)
```

* HAWAIAN
```{r}
qplot(HAWAIAN,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for HAWAIAN", 
      xlab = "HAWAIAN",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(HAWAIAN,
  main = "HAWAIAN",
  xlab = "Count",
  ylab = "HAWAIAN",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(HAWAIAN), 
     main="HAWAIAN DISTRIBUTION")
polygon(density(HAWAIAN), col="pink", border="blue")


plot(HAWAIAN, EARNINGS)
```

* BI_RACIAL
```{r}
qplot(BI_RACIAL,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for BI_RACIAL", 
      xlab = "BI_RACIAL",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(BI_RACIAL,
  main = "BI_RACIAL",
  xlab = "Count",
  ylab = "BI_RACIAL",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(BI_RACIAL), 
     main="BI_RACIAL DISTRIBUTION")
polygon(density(BI_RACIAL), col="pink", border="blue")


plot(BI_RACIAL, EARNINGS)
```

* MULTI_RACIAL
```{r}
qplot(MULTI_RACIAL,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for MULTI_RACIAL", 
      xlab = "MULTI_RACIAL",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(MULTI_RACIAL,
  main = "MULTI_RACIAL",
  xlab = "Count",
  ylab = "MULTI_RACIAL",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(MULTI_RACIAL), 
     main="MULTI_RACIAL DISTRIBUTION")
polygon(density(MULTI_RACIAL), col="pink", border="blue")


plot(MULTI_RACIAL, EARNINGS)
```

* WELFARE
```{r}
qplot(WELFARE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for WELFARE", 
      xlab = "WELFARE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(WELFARE,
  main = "WELFARE",
  xlab = "Count",
  ylab = "WELFARE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(WELFARE), 
     main="WELFARE DISTRIBUTION")
polygon(density(WELFARE), col="pink", border="blue")


plot(WELFARE, EARNINGS)
```

# ----------------------RAW_LIMITED---------------------
```{r}
colnames(RAW_LIMITED)
```
* RT
```{r}
qplot(RAW_LIMITED$RT,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for RT", 
      xlab = "RT", 
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$RT,
  main = "RT",
  xlab = "Count",
  ylab = "RT",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$RT), 
     main="RT DISTRIBUTION")
polygon(density(RT), col="pink", border="blue")


plot(RT, EARNINGS)
```

* SERIALNO
```{r}
qplot(RAW_LIMITED$SERIALNO,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for DOC_EDU", 
      xlab = "SERIALNO",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$SERIALNO,
  main = "SERIALNO",
  xlab = "Count",
  ylab = "SERIALNO",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$SERIALNO), 
     main="SERIALNO DISTRIBUTION")
polygon(density(RAW_LIMITED$SERIALNO), col="pink", border="blue")


plot(RAW_LIMITED$SERIALNO, RAW_LIMITED$EARNINGS)
```

* AGE
```{r}
qplot(RAW_LIMITED$AGE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for AGE", 
      xlab = "AGE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$AGE,
  main = "AGE",
  xlab = "Count",
  ylab = "AGE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$AGE), 
     main="AGE DISTRIBUTION")
polygon(density(RAW_LIMITED$AGE), col="pink", border="blue")


plot(RAW_LIMITED$AGE, RAW_LIMITED$EARNINGS)
```

* CITIZENSHIP
```{r}
qplot(RAW_LIMITED$CITIZENSHIP,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for CITIZENSHIP", 
      xlab = "CITIZENSHIP",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$CITIZENSHIP,
  main = "CITIZENSHIP",
  xlab = "Count",
  ylab = "CITIZENSHIP",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$CITIZENSHIP), 
     main="CITIZENSHIP DISTRIBUTION")
polygon(density(RAW_LIMITED$CITIZENSHIP), col="pink", border="blue")


plot(RAW_LIMITED$CITIZENSHIP, RAW_LIMITED$EARNINGS)
```

* WORKER_CLASS
```{r}
qplot(RAW_LIMITED$WORKER_CLASS,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for WORKER_CLASS", 
      xlab = "WORKER_CLASS",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$WORKER_CLASS,
  main = "WORKER_CLASS",
  xlab = "Count",
  ylab = "WORKER_CLASS",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$WORKER_CLASS), 
     main="WORKER_CLASS DISTRIBUTION")
polygon(density(RAW_LIMITED$WORKER_CLASS), col="pink", border="blue")


plot(RAW_LIMITED$WORKER_CLASS, RAW_LIMITED$EARNINGS)
```

* ENGLISH_ABILITY
```{r}
qplot(RAW_LIMITED$ENGLISH_ABILITY,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for ENGLISH_ABILITY", 
      xlab = "ENGLISH_ABILITY",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$ENGLISH_ABILITY,
  main = "ENGLISH_ABILITY",
  xlab = "Count",
  ylab = "ENGLISH_ABILITY",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$ENGLISH_ABILITY), 
     main="ENGLISH_ABILITY DISTRIBUTION")
polygon(density(RAW_LIMITED$ENGLISH_ABILITY), col="pink", border="blue")


plot(RAW_LIMITED$ENGLISH_ABILITY, RAW_LIMITED$EARNINGS)
```

* OTHER_LANGUAGE
```{r}
qplot(RAW_LIMITED$OTHER_LANGUAGE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for OTHER_LANGUAGE", 
      xlab = "OTHER_LANGUAGE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$OTHER_LANGUAGE,
  main = "OTHER_LANGUAGE",
  xlab = "Count",
  ylab = "OTHER_LANGUAGE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$OTHER_LANGUAGE), 
     main="OTHER_LANGUAGE DISTRIBUTION")
polygon(density(RAW_LIMITED$OTHER_LANGUAGE), col="pink", border="blue")


plot(RAW_LIMITED$OTHER_LANGUAGE, RAW_LIMITED$EARNINGS)
```

* MAR_STATUS
```{r}
qplot(RAW_LIMITED$MAR_STATUS,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for MAR_STATUS", 
      xlab = "MAR_STATUS",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$MAR_STATUS,
  main = "MAR_STATUS",
  xlab = "Count",
  ylab = "MAR_STATUS",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$MAR_STATUS), 
     main="MAR_STATUS DISTRIBUTION")
polygon(density(RAW_LIMITED$MAR_STATUS), col="pink", border="blue")


plot(RAW_LIMITED$MAR_STATUS, RAW_LIMITED$EARNINGS)
```

* EDU_LEVEL
```{r}
qplot(RAW_LIMITED$EDU_LEVEL,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for EDU_LEVEL", 
      xlab = "EDU_LEVEL",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$EDU_LEVEL,
  main = "EDU_LEVEL",
  xlab = "Count",
  ylab = "EDU_LEVEL",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$EDU_LEVEL), 
     main="EDU_LEVEL DISTRIBUTION")
polygon(density(RAW_LIMITED$EDU_LEVEL), col="pink", border="blue")


plot(RAW_LIMITED$EDU_LEVEL, RAW_LIMITED$EARNINGS)
```

* SEX
```{r}
qplot(RAW_LIMITED$SEX,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SEX", 
      xlab = "SEX",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$SEX,
  main = "SEX",
  xlab = "Count",
  ylab = "SEX",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$SEX), 
     main="SEX DISTRIBUTION")
polygon(density(RAW_LIMITED$SEX), col="pink", border="blue")


plot(RAW_LIMITED$SEX, RAW_LIMITED$EARNINGS)
```

* SUPP_INC
```{r}
qplot(RAW_LIMITED$SUPP_INC,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SUPP_INC", 
      xlab = "SUPP_INC",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$SUPP_INC,
  main = "SUPP_INC",
  xlab = "Count",
  ylab = "SUPP_INC",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$SUPP_INC), 
     main="SUPP_INC DISTRIBUTION")
polygon(density(RAW_LIMITED$SUPP_INC), col="pink", border="blue")


plot(RAW_LIMITED$SUPP_INC, RAW_LIMITED$EARNINGS)
```

* SOCIAL_SECURITY
```{r}
qplot(RAW_LIMITED$SOCIAL_SECURITY,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SOCIAL_SECURITY", 
      xlab = "SOCIAL_SECURITY",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$SOCIAL_SECURITY,
  main = "SOCIAL_SECURITY",
  xlab = "Count",
  ylab = "SOCIAL_SECURITY",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$SOCIAL_SECURITY), 
     main="SOCIAL_SECURITY DISTRIBUTION")
polygon(density(RAW_LIMITED$SOCIAL_SECURITY), col="pink", border="blue")


plot(RAW_LIMITED$SOCIAL_SECURITY, RAW_LIMITED$EARNINGS)
```

* WAGE
```{r}
qplot(RAW_LIMITED$WAGE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for WAGE", 
      xlab = "WAGE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$WAGE,
  main = "WAGE",
  xlab = "Count",
  ylab = "WAGE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$WAGE), 
     main="WAGE DISTRIBUTION")
polygon(density(RAW_LIMITED$WAGE), col="pink", border="blue")


plot(RAW_LIMITED$WAGE, RAW_LIMITED$EARNINGS)
```

* HOURS_WORKED
```{r}
qplot(RAW_LIMITED$HOURS_WORKED,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for HOURS_WORKED", 
      xlab = "HOURS_WORKED",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$HOURS_WORKED,
  main = "HOURS_WORKED",
  xlab = "Count",
  ylab = "HOURS_WORKED",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$HOURS_WORKED), 
     main="HOURS_WORKED DISTRIBUTION")
polygon(density(RAW_LIMITED$HOURS_WORKED), col="pink", border="blue")


plot(RAW_LIMITED$HOURS_WORKED, RAW_LIMITED$EARNINGS)
```

* WEEKS_WORKED
```{r}
qplot(RAW_LIMITED$WEEKS_WORKED,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for WEEKS_WORKED", 
      xlab = "WEEKS_WORKED",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$WEEKS_WORKED,
  main = "WEEKS_WORKED",
  xlab = "Count",
  ylab = "WEEKS_WORKED",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$WEEKS_WORKED), 
     main="WEEKS_WORKED DISTRIBUTION")
polygon(density(RAW_LIMITED$WEEKS_WORKED), col="pink", border="blue")


plot(RAW_LIMITED$WEEKS_WORKED, RAW_LIMITED$EARNINGS)
```

* DISABILITY
```{r}
qplot(RAW_LIMITED$DISABILITY,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for DISABILITY", 
      xlab = "DISABILITY",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$DISABILITY,
  main = "DISABILITY",
  xlab = "Count",
  ylab = "DISABILITY",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$DISABILITY), 
     main="DISABILITY DISTRIBUTION")
polygon(density(RAW_LIMITED$DISABILITY), col="pink", border="blue")


plot(RAW_LIMITED$DISABILITY, RAW_LIMITED$EARNINGS)
```

* EMPLOYMENT
```{r}
qplot(RAW_LIMITED$EMPLOYMENT,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for EMPLOYMENT", 
      xlab = "EMPLOYMENT",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$EMPLOYMENT,
  main = "EMPLOYMENT",
  xlab = "Count",
  ylab = "EMPLOYMENT",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$EMPLOYMENT), 
     main="EMPLOYMENT DISTRIBUTION")
polygon(density(RAW_LIMITED$EMPLOYMENT), col="pink", border="blue")


plot(RAW_LIMITED$EMPLOYMENT, RAW_LIMITED$EARNINGS)
```

* NATIVITY
```{r}
qplot(RAW_LIMITED$NATIVITY,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for NATIVITY", 
      xlab = "NATIVITY",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$NATIVITY,
  main = "NATIVITY",
  xlab = "Count",
  ylab = "NATIVITY",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$NATIVITY), 
     main="NATIVITY DISTRIBUTION")
polygon(density(RAW_LIMITED$NATIVITY), col="pink", border="blue")


plot(RAW_LIMITED$NATIVITY, RAW_LIMITED$EARNINGS)
```

* SECOND_GEN
```{r}
qplot(RAW_LIMITED$SECOND_GEN,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for SECOND_GEN", 
      xlab = "SECOND_GEN",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$SECOND_GEN,
  main = "SECOND_GEN",
  xlab = "Count",
  ylab = "SECOND_GEN",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$SECOND_GEN), 
     main="SECOND_GEN DISTRIBUTION")
polygon(density(RAW_LIMITED$SECOND_GEN), col="pink", border="blue")


plot(RAW_LIMITED$SECOND_GEN, RAW_LIMITED$EARNINGS)
```

* CHILDREN
```{r}
qplot(RAW_LIMITED$CHILDREN,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for CHILDREN", 
      xlab = "CHILDREN",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$CHILDREN,
  main = "CHILDREN",
  xlab = "Count",
  ylab = "CHILDREN",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$CHILDREN), 
     main="CHILDREN DISTRIBUTION")
polygon(density(RAW_LIMITED$CHILDREN), col="pink", border="blue")


plot(RAW_LIMITED$CHILDREN, RAW_LIMITED$EARNINGS)
```

* INCOME
```{r}
qplot(RAW_LIMITED$INCOME,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for INCOME", 
      xlab = "INCOME",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$INCOME,
  main = "INCOME",
  xlab = "Count",
  ylab = "INCOME",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$INCOME), 
     main="INCOME DISTRIBUTION")
polygon(density(RAW_LIMITED$INCOME), col="pink", border="blue")


plot(RAW_LIMITED$INCOME, RAW_LIMITED$EARNINGS)
```

* RACE
```{r}
qplot(RAW_LIMITED$RACE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for RACE", 
      xlab = "RACE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$RACE,
  main = "RACE",
  xlab = "Count",
  ylab = "RACE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$RACE), 
     main="RACE DISTRIBUTION")
polygon(density(RAW_LIMITED$RACE), col="pink", border="blue")


plot(RAW_LIMITED$RACE, RAW_LIMITED$EARNINGS)
```
