---
title: R Notebook
output: html_notebook
---


```{r}
rm(list=ls(all=TRUE))
```


```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(corrplot)
library(stargazer)
library(tidyr)
library(tidyverse)
library(ggplot2)
```

```{r}
raw_dat <- read.csv('Raw_Project_Data_2.csv')
```

```{r}
summary(raw_dat)
```

```{r}
dummy_dat = data.frame(
  # citizenship
  born_citizen = if_else(raw_dat$CITIZENSHIP == 1, 1, if_else(raw_dat$CITIZENSHIP == 2, 1, if_else(raw_dat$CITIZENSHIP == 3, 1, 0))),
  naturalized_citizen = if_else(raw_dat$CITIZENSHIP == 4, 1, 0),
  not_citizen = if_else(raw_dat$CITIZENSHIP == 5, 1, 0),
  
  # worker classification
  INLF = if_else(raw_dat$WORKER_CLASS == 'b', 1, 0),
  private_sector = if_else(raw_dat$WORKER_CLASS == 1, 1, 0),
  gov_sector = if_else(raw_dat$WORKER_CLASS == 2, 1, if_else(raw_dat$WORKER_CLASS == 3, 1, if_else(raw_dat$WORKER_CLASS == 4, 1, if_else(raw_dat$WORKER_CLASS == 5, 1, 0)))),
  self_employed = if_else(raw_dat$WORKER_CLASS == 5, 1, if_else(raw_dat$WORKER_CLASS == 6, 1, 0)),
  without_pay = if_else(raw_dat$WORKER_CLASS == 8, 1, 0),
  unemployed = if_else(raw_dat$WORKER_CLASS == 9, 1, 0),
  
  # ability to speak english
  under5_english = if_else(raw_dat$ENGLISH_ABILITY == 'b', 1, 0),
  eng_very_well = if_else(raw_dat$ENGLISH_ABILITY == 1, 1, 0),
  eng_well = if_else(raw_dat$ENGLISH_ABILITY == 2, 1, 0),
  eng_not_well = if_else(raw_dat$ENGLISH_ABILITY == 3, 1, 0),
  eng_none = if_else(raw_dat$ENGLISH_ABILITY == 4, 1, 0),
  
  # bi-lingual
  under5_multi = if_else(raw_dat$OTHER_LANGUAGE == 'b', 1, 0),
  multilingual = if_else(raw_dat$OTHER_LANGUAGE == 1, 1, 0),
  
  # martial status
  married = if_else(raw_dat$MAR_STATUS == 1, 1, 0),
  widowed = if_else(raw_dat$MAR_STATUS == 2, 1, 0),
  divorced = if_else(raw_dat$MAR_STATUS == 3, 1, 0),
  separated = if_else(raw_dat$MAR_STATUS == 4, 1, 0),
  single = if_else(raw_dat$MAR_STATUS == 5, 1, 0),

  # educational obtainment
  under_5_edu = if_else(raw_dat$EDU_LEVEL == 'bb', 1, 0),
  uncomplete_edu = if_else(raw_dat$EDU_LEVEL == 01, 1, 0),
  primary_edu = if_else(raw_dat$EDU_LEVEL == 03, 1, if_else(raw_dat$EDU_LEVEL == 04, 1, if_else(raw_dat$EDU_LEVEL == 05, 1, if_else(raw_dat$EDU_LEVEL == 06, 1, if_else(raw_dat$EDU_LEVEL == 07, 1, if_else(raw_dat$EDU_LEVEL == 08, 1, if_else(raw_dat$EDU_LEVEL == 09, 1, if_else(raw_dat$EDU_LEVEL == 10, 1, if_else(raw_dat$EDU_LEVEL == 11, 1, 0))))))))),
  secondary_edu = if_else(raw_dat$EDU_LEVEL == 15, 1, 0),
  secondary_diploma = if_else(raw_dat$EDU_LEVEL == 16, 1, 0),
  secondary_complete = if_else(raw_dat$EDU_LEVEL == 15, 1, if_else(raw_dat$EDU_LEVEL == 16, 1, if_else(raw_dat$EDU_LEVEL == 17, 1, 0))),
  GED = if_else(raw_dat$EDU_LEVEL == 17, 1,0),
  some_secondary = if_else(raw_dat$EDU_LEVEL == 12, 1, if_else(raw_dat$EDU_LEVEL == 13, 1,if_else(raw_dat$EDU_LEVEL == 14, 1, if_else(raw_dat$EDU_LEVEL == 15, 1, 0)))),
  associates = if_else(raw_dat$EDU_LEVEL == 20, 1, 0),
  bachelors = if_else(raw_dat$EDU_LEVEL == 21, 1, 0),
  some_college = if_else(raw_dat$EDU_LEVEL == 18, 1, if_else(raw_dat$EDU_LEVEL == 19, 1, 0)),
  masters = if_else(raw_dat$EDU_LEVEL == 22, 1, 0),
  professional = if_else(raw_dat$EDU_LEVEL == 23, 1, 0),
  doctoral = if_else(raw_dat$EDU_LEVEL == 24, 1, 0),
  
  # sex
  male = if_else(raw_dat$SEX == 1, 1, 0),
  female = if_else(raw_dat$SEX == 2, 1, 0),
  
  # disability
  disability_dummy = if_else(raw_dat$DISABILITY == 1, 1, 0),
  
  # nativity
  nativity_dummy = if_else(raw_dat$NATIVITY == 1, 1, 0),
  
  # nativity of parents
  not_child = if_else(raw_dat$SECOND_GEN == 'b', 1, 0),
  not_second = if_else(raw_dat$SECOND_GEN == 1, 1, if_else(raw_dat$SECOND_GEN == 5, 1, if_else(raw_dat$SECOND_GEN == 7, 1, 0))),
  second_gen_dummy = if_else(raw_dat$SECOND_GEN == 2, 1, if_else(raw_dat$SECOND_GEN == 3, 1, if_else(raw_dat$SECOND_GEN == 4, 1, if_else(raw_dat$SECOND_GEN == 6, 1, if_else(raw_dat$SECOND_GEN == 8, 1, 0)))))
)
```

### REMOVE SECOND GEN VARIABLE, OVER 118K NAs
### REMOVE ENGLISH ABILITY, ~ 90K NAs
### REMOVE UNEMP, NOT_LB ~ REMOVED BECAUSE DATASET IS LIMITED TO EMPLOYED
### REMOVING UNDER_EDU, UNDER MULTI ~ LIMITED TO EMPLOYED BECAUSE DATASET IS LIMITED TO EMPLOYED, MINORS UNDER 16 CANNOT LEGALLY BE EMPLOYED


```{r}
FIN_DAT <- dummy_dat
```

```{r}
FIN_DAT$EARNINGS <- raw_dat$EARNINGS
FIN_DAT$INCOME <- raw_dat$INCOME
FIN_DAT$WAGE <- raw_dat$WAGE
FIN_DAT$AGE <- raw_dat$AGE
FIN_DAT$SUPP_INC <- raw_dat$SUPP_INC 
FIN_DAT$SOCIAL_SECURITY <- raw_dat$SOCIAL_SECURITY 
FIN_DAT$HR_WORKED <- raw_dat$HOURS_WORKED 
FIN_DAT$WK_WORKED <- raw_dat$WEEKS_WORKED 
```

```{r}
FIN_DAT$SERIEL_NO <- FIN_DAT$SERIALNO 
FIN_DAT$EARNINGS <- FIN_DAT$EARNINGS
FIN_DAT$INCOME <- FIN_DAT$INCOME
FIN_DAT$WAGE <- FIN_DAT$WAGE
FIN_DAT$AGE <- FIN_DAT$AGE 
FIN_DAT$SUPP_INC <- FIN_DAT$SUPP_INC 
FIN_DAT$SOCIAL_SECURITY <- FIN_DAT$SOCIAL_SECURITY 
FIN_DAT$HR_WORKED <- FIN_DAT$HOURS_WORKED 
FIN_DAT$WK_WORKED <- FIN_DAT$WEEKS_WORKED 
FIN_DAT$B_CIT <- FIN_DAT$born_citizen 
FIN_DAT$NAT_CIT <- FIN_DAT$naturalized_citizen 
FIN_DAT$NOT_CIT <- FIN_DAT$not_citizen 
FIN_DAT$NOT_LB <- FIN_DAT$INLF 
FIN_DAT$PRI_SEC <- FIN_DAT$private_sector 
FIN_DAT$GOV_SEC <- FIN_DAT$gov_sector 
FIN_DAT$SELF_EMP <- FIN_DAT$self_employed 
FIN_DAT$WRK_UNPAID <- FIN_DAT$without_pay 
FIN_DAT$UNEMP <- FIN_DAT$unemployed 
FIN_DAT$UNDER_ENG <- FIN_DAT$under5_english 
FIN_DAT$ENG_VW <- FIN_DAT$ eng_very_well 
FIN_DAT$ENG_W <- FIN_DAT$eng_well 
FIN_DAT$ENG_NW <- FIN_DAT$eng_not_well 
FIN_DAT$ENG_NON <- FIN_DAT$eng_none 
FIN_DAT$UNDER_MULTI <- FIN_DAT$under5_multi 
FIN_DAT$MULTI <- FIN_DAT$ multilingual 
FIN_DAT$MARRIED <- FIN_DAT$ married 
FIN_DAT$WIDOWED <- FIN_DAT$widowed 
FIN_DAT$DIVORCED <- FIN_DAT$divorced 
FIN_DAT$SEPARATED <- FIN_DAT$separated 
FIN_DAT$NOT_MARRIED <- FIN_DAT$not_married 
FIN_DAT$UNDER_EDU <- FIN_DAT$under_5_edu 
FIN_DAT$INCOMP_EDU <- FIN_DAT$uncomplete_edu 
FIN_DAT$PRIM_EDU <- FIN_DAT$primary_edu 
FIN_DAT$SEC_INCOMP <- FIN_DAT$secondary_edu 
FIN_DAT$SEC_DIP <- FIN_DAT$secondary_diploma 
FIN_DAT$SEC_EDU <- FIN_DAT$secondary_complete 
FIN_DAT$GED_EDU <- FIN_DAT$GED 
FIN_DAT$SOME_SEC <- FIN_DAT$some_secondary 
FIN_DAT$AST_EDU <- FIN_DAT$associates
FIN_DAT$BACH_EDU <- FIN_DAT$bachelors 
FIN_DAT$SOME_COL <- FIN_DAT$some_college 
FIN_DAT$MAST_EDU <- FIN_DAT$ masters 
FIN_DAT$PROF_EDU <- FIN_DAT$professional 
FIN_DAT$DOC_EDU <- FIN_DAT$doctoral 
FIN_DAT$MALE <- FIN_DAT$male 
FIN_DAT$FEMALE <- FIN_DAT$female 
FIN_DAT$DISABILITY <- FIN_DAT$disability_dummy 
FIN_DAT$NATIVITY <- FIN_DAT$nativity_dummy 
FIN_DAT$NOT_CHILD <- FIN_DAT$not_child 
FIN_DAT$NOT_SEC <- FIN_DAT$not_second 
FIN_DAT$SEC_GEN <- FIN_DAT$second_gen_dummy
```

```{r}
RAW_LIMITED <- subset(raw_dat, EARNINGS > 0 & EARNINGS < 463000 & AGE >= 18)

NEW_DAT <- subset(FIN_DAT, EARNINGS > 0 & EARNINGS < 463000 & AGE >= 18)

```


```{r}
summary(NEW_DAT)
```


```{r}
attach(NEW_DAT)
```

### NO LONGER HAVE TO USE "FIN_DAT$" TO CALL VARIABLE. JUST USE VARIABLE NAME ALONE.
#### E.G.: "FIN_DAT$EARNINGS" BECOMES "EARNINGS

```{r}
qplot(EARNINGS,
      geom="histogram",
      binwidth = 10000,  
      main = "Histogram for EARNINGS", 
      xlab = "EARNINGS",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(EARNINGS,
  main = "EARNINGS",
  xlab = "Count",
  ylab = "EARNINGS",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(EARNINGS), 
     main="EARNINGS DISTRIBUTION")
polygon(density(EARNINGS), col="pink", border="blue")

plot(EARNINGS)

round(mean(EARNINGS), 0)
median(EARNINGS)
round(sqrt(var(EARNINGS, y = NULL)))
min(EARNINGS)
max(EARNINGS)


```


```{r}
qplot(AGE,
      geom="histogram",
      binwidth = 5,  
      main = "Histogram for Age", 
      xlab = "Age",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(AGE,
  main = "Age",
  xlab = "Count",
  ylab = "Age",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(AGE), 
     main="AGE DISTRIBUTION")
polygon(density(AGE), col="pink", border="blue")


plot(AGE, EARNINGS)

round(mean(AGE), 0)
median(AGE)
round(sqrt(var(AGE, y = NULL)))
min(AGE)
max(AGE)
```

```{r}
qplot(RAW_LIMITED$CITIZENSHIP,
      geom="histogram",
      binwidth = 1,  
      main = "Histogram for CITIZENSHIP", 
      xlab = "CITIZENSHIP",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(AGE,
  main = "CITIZENSHIP",
  xlab = "Count",
  ylab = "CITIZENSHIP",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$CITIZENSHIP), 
     main="CITIZENSHIP DISTRIBUTION")
polygon(density(RAW_LIMITED$CITIZENSHIP), col="pink", border="blue")


plot(RAW_LIMITED$CITIZENSHIP, EARNINGS)

round(mean(RAW_LIMITED$CITIZENSHIP), 0)
(mean(RAW_LIMITED$CITIZENSHIP))
median(RAW_LIMITED$CITIZENSHIP)
round(sqrt(var(RAW_LIMITED$CITIZENSHIP, y = NULL)))
(sqrt(var(RAW_LIMITED$CITIZENSHIP, y = NULL)))
min(RAW_LIMITED$CITIZENSHIP)
max(RAW_LIMITED$CITIZENSHIP)
```

```{r}
qplot(RAW_LIMITED$WORKER_CLASS,
      geom="histogram",
      binwidth = 1,  
      main = "Histogram for WORKER_CLASS", 
      xlab = "WORKER_CLASS",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(AGE,
  main = "WORKER_CLASS",
  xlab = "Count",
  ylab = "WORKER_CLASS",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$WORKER_CLASS), 
     main="WORKER_CLASS DISTRIBUTION")
polygon(density(RAW_LIMITED$WORKER_CLASS), col="pink", border="blue")

plot(RAW_LIMITED$WORKER_CLASS, EARNINGS)

round(mean(RAW_LIMITED$WORKER_CLASS), 0)
(mean(RAW_LIMITED$WORKER_CLASS))
median(RAW_LIMITED$WORKER_CLASS)
round(sqrt(var(RAW_LIMITED$WORKER_CLASS, y = NULL)))
(sqrt(var(RAW_LIMITED$WORKER_CLASS, y = NULL)))
min(RAW_LIMITED$WORKER_CLASS)
max(RAW_LIMITED$WORKER_CLASS)
```

```{r}
qplot(RAW_LIMITED$OTHER_LANGUAGE,
      geom="histogram",
      binwidth = 1,  
      main = "Histogram for OTHER_LANGUAGE", 
      xlab = "OTHER_LANGUAGE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$OTHER_LANGUAGE,
  main = "OTHER_LANGUAGE",
  xlab = "Count",
  ylab = "OTHER_LANGUAGE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$OTHER_LANGUAGE), 
     main="OTHER_LANGUAGE DISTRIBUTION")
polygon(density(RAW_LIMITED$OTHER_LANGUAGE), col="pink", border="blue")

plot(RAW_LIMITED$WORKER_CLASS, EARNINGS)

round(mean(RAW_LIMITED$WORKER_CLASS), 0)
(mean(RAW_LIMITED$WORKER_CLASS))
median(RAW_LIMITED$WORKER_CLASS)
round(sqrt(var(RAW_LIMITED$WORKER_CLASS, y = NULL)))
(sqrt(var(RAW_LIMITED$WORKER_CLASS, y = NULL)))
min(RAW_LIMITED$WORKER_CLASS)
max(RAW_LIMITED$WORKER_CLASS)
```

```{r}
qplot(RAW_LIMITED$MAR_STATUS,
      geom="histogram",
      binwidth = 1,  
      main = "Histogram for MAR_STATUS", 
      xlab = "MAR_STATUS",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

plot(density(RAW_LIMITED$MAR_STATUS), 
     main="MAR_STATUS DISTRIBUTION")
polygon(density(RAW_LIMITED$MAR_STATUS), col="pink", border="blue")

barplot(table(RAW_LIMITED$MAR_STATUS)[order(table(RAW_LIMITED$MAR_STATUS))],
        main="RAW_LIMITED$MAR_STATUS",
        xlab = "MAR_STATUS",
        srt = 45, 
        cex.names = 0.65, 
        fill=I("chartreuse"),
        col=I("cornflowerblue"))

boxplot(RAW_LIMITED$MAR_STATUS,
  main = "MAR_STATUS",
  xlab = "Count",
  ylab = "MAR_STATUS",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(RAW_LIMITED$MAR_STATUS, EARNINGS)

round(mean(RAW_LIMITED$MAR_STATUS), 0)
(mean(RAW_LIMITED$MAR_STATUS))
median(RAW_LIMITED$MAR_STATUS)
round(sqrt(var(RAW_LIMITED$MAR_STATUS, y = NULL)))
(sqrt(var(RAW_LIMITED$MAR_STATUS, y = NULL)))
min(RAW_LIMITED$MAR_STATUS)
max(RAW_LIMITED$MAR_STATUS)
```

```{r}
qplot(RAW_LIMITED$EDU_LEVEL,
      geom="histogram",
      binwidth = 1,  
      main = "Histogram for EDU_LEVEL", 
      xlab = "EDU_LEVEL",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

plot(density(RAW_LIMITED$EDU_LEVEL), 
     main="EDU_LEVEL DISTRIBUTION")
polygon(density(RAW_LIMITED$EDU_LEVEL), col="pink", border="blue")

barplot(table(RAW_LIMITED$EDU_LEVEL)[order(table(RAW_LIMITED$EDU_LEVEL))],
        main="RAW_LIMITED$EDU_LEVEL",
        xlab = "EDU_LEVEL",
        srt = 45, 
        cex.names = 0.65, 
        fill=I("chartreuse"),
        col=I("cornflowerblue"))

boxplot(RAW_LIMITED$EDU_LEVEL,
  main = "EDU_LEVEL",
  xlab = "Count",
  ylab = "EDU_LEVEL",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(RAW_LIMITED$EDU_LEVEL, EARNINGS)

round(mean(RAW_LIMITED$EDU_LEVEL), 0)
(mean(RAW_LIMITED$EDU_LEVEL))
median(RAW_LIMITED$EDU_LEVEL)
round(sqrt(var(RAW_LIMITED$EDU_LEVEL, y = NULL)))
(sqrt(var(RAW_LIMITED$EDU_LEVEL, y = NULL)))
min(RAW_LIMITED$EDU_LEVEL)
max(RAW_LIMITED$EDU_LEVEL)
```

```{r}
qplot(RAW_LIMITED$SEX,
      geom="histogram",
      binwidth = 1,  
      main = "Histogram for SEX", 
      xlab = "SEX",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

plot(density(RAW_LIMITED$SEX), 
     main="SEX DISTRIBUTION")
polygon(density(RAW_LIMITED$SEX), col="pink", border="blue")

boxplot(RAW_LIMITED$SEX,
  main = "SEX",
  xlab = "Count",
  ylab = "SEX",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(RAW_LIMITED$SEX, EARNINGS)

round(mean(RAW_LIMITED$SEX), 0)
(mean(RAW_LIMITED$SEX))
median(RAW_LIMITED$SEX)
round(sqrt(var(RAW_LIMITED$SEX, y = NULL)))
(sqrt(var(RAW_LIMITED$SEX, y = NULL)))
min(RAW_LIMITED$SEX)
max(RAW_LIMITED$SEX)
```

```{r}
qplot(RAW_LIMITED$SUPP_INC,
      geom="histogram",
      binwidth = 1000,  
      main = "Histogram for SUPP_INC", 
      xlab = "SUPP_INC",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

plot(density(RAW_LIMITED$SUPP_INC), 
     main="SUPP_INC DISTRIBUTION")
polygon(density(RAW_LIMITED$SUPP_INC), col="pink", border="blue")

barplot(table(RAW_LIMITED$SUPP_INC)[order(table(RAW_LIMITED$SUPP_INC))],
        main="RAW_LIMITED$SUPP_INC",
        xlab = "SUPP_INC",
        srt = 45, 
        cex.names = 0.65, 
        fill=I("chartreuse"),
        col=I("cornflowerblue"))

boxplot(RAW_LIMITED$SUPP_INC,
  main = "SUPP_INC",
  xlab = "Count",
  ylab = "SUPP_INC",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(RAW_LIMITED$SUPP_INC, EARNINGS)

round(mean(RAW_LIMITED$SUPP_INC), 0)
(mean(RAW_LIMITED$SUPP_INC))
median(RAW_LIMITED$SUPP_INC)
round(sqrt(var(RAW_LIMITED$SUPP_INC, y = NULL)))
(sqrt(var(RAW_LIMITED$SUPP_INC, y = NULL)))
min(RAW_LIMITED$SUPP_INC)
max(RAW_LIMITED$SUPP_INC)
```


```{r}
qplot(SOCIAL_SECURITY,
      geom="histogram",
      binwidth = 1000,  
      main = "Histogram for SOCIAL_SECURITY", 
      xlab = "SOCIAL_SECURITY",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

plot(density(SOCIAL_SECURITY), 
     main="SOCIAL_SECURITY DISTRIBUTION")
polygon(density(SOCIAL_SECURITY), col="pink", border="blue")

barplot(table(RAW_LIMITED$SUPP_INC)[order(table(RAW_LIMITED$SUPP_INC))],
        main="RAW_LIMITED$SUPP_INC",
        xlab = "SUPP_INC",
        srt = 45, 
        cex.names = 0.65, 
        fill=I("chartreuse"),
        col=I("cornflowerblue"))

boxplot(SOCIAL_SECURITY,
  main = "SOCIAL_SECURITY",
  xlab = "Count",
  ylab = "SOCIAL_SECURITY",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(SOCIAL_SECURITY, EARNINGS)

round(mean(SOCIAL_SECURITY), 0)
(mean(SOCIAL_SECURITY))
median(SOCIAL_SECURITY)
round(sqrt(var(SOCIAL_SECURITY, y = NULL)))
(sqrt(var(SOCIAL_SECURITY, y = NULL)))
min(SOCIAL_SECURITY)
max(SOCIAL_SECURITY)
```


```{r}
qplot(WAGE,
      geom="histogram",
      binwidth = 10000,  
      main = "Histogram for WAGE", 
      xlab = "WAGE",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )


plot(density(WAGE), 
     main="WAGE DISTRIBUTION")
polygon(density(WAGE), col="pink", border="blue")

barplot(table(WAGE)[order(table(WAGE))],
        main="WAGE",
        xlab = "WAGE",
        srt = 45, 
        cex.names = 0.65, 
        fill=I("chartreuse"),
        col=I("cornflowerblue"))

boxplot(WAGE,
  main = "WAGE",
  xlab = "Count",
  ylab = "WAGE",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(WAGE, EARNINGS)

round(mean(WAGE), 0)
(mean(WAGE))
median(WAGE)
round(sqrt(var(WAGE, y = NULL)))
(sqrt(var(WAGE, y = NULL)))
min(WAGE)
max(WAGE)
```


```{r}
qplot(RAW_LIMITED$HOURS_WORKED,
      geom="histogram",
      binwidth = 10,  
      main = "Histogram for HOURS_WORKED", 
      xlab = "HOURS_WORKED",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

plot(density(RAW_LIMITED$HOURS_WORKED), 
     main="OTHER_LANGUAGE DISTRIBUTION")
polygon(density(RAW_LIMITED$HOURS_WORKED), col="pink", border="blue")

barplot(table(RAW_LIMITED$HOURS_WORKED)[order(table(RAW_LIMITED$HOURS_WORKED))],
        main="WAGE",
        xlab = "WAGE",
        srt = 45, 
        cex.names = 0.65, 
        fill=I("chartreuse"),
        col=I("cornflowerblue"))

boxplot(RAW_LIMITED$HOURS_WORKED,
  main = "HR_WORKED",
  xlab = "Count",
  ylab = "HR_WORKED",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(RAW_LIMITED$HOURS_WORKED, EARNINGS)

round(mean(RAW_LIMITED$HOURS_WORKED), 0)
(mean(RAW_LIMITED$HOURS_WORKED))
median(RAW_LIMITED$HOURS_WORKED)
round(sqrt(var(RAW_LIMITED$HOURS_WORKED, y = NULL)))
(sqrt(var(RAW_LIMITED$HOURS_WORKED, y = NULL)))
min(RAW_LIMITED$HOURS_WORKED)
max(RAW_LIMITED$HOURS_WORKED)
```


```{r}
qplot(RAW_LIMITED$WEEKS_WORKED,
      geom="histogram",
      binwidth = 1,  
      main = "Histogram for WEEKS_WORKED", 
      xlab = "WEEKS_WORKED",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

plot(density(RAW_LIMITED$WEEKS_WORKED), 
     main="WEEKS_WORKED DISTRIBUTION")
polygon(density(RAW_LIMITED$WEEKS_WORKED), col="pink", border="blue")

barplot(table(RAW_LIMITED$WEEKS_WORKED)[order(table(RAW_LIMITED$WEEKS_WORKED))],
        main="WK_WORKED",
        xlab = "WK_WORKED",
        srt = 45, 
        cex.names = 0.65, 
        fill=I("chartreuse"),
        col=I("cornflowerblue"))

boxplot(RAW_LIMITED$WEEKS_WORKED,
  main = "WK_WORKED",
  xlab = "Count",
  ylab = "WK_WORKED",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(RAW_LIMITED$WEEKS_WORKED, EARNINGS)

round(mean(RAW_LIMITED$WEEKS_WORKED), 0)
(mean(RAW_LIMITED$WEEKS_WORKED))
median(RAW_LIMITED$WEEKS_WORKED)
round(sqrt(var(RAW_LIMITED$WEEKS_WORKED, y = NULL)))
(sqrt(var(RAW_LIMITED$WEEKS_WORKED, y = NULL)))
min(RAW_LIMITED$WEEKS_WORKED)
max(RAW_LIMITED$WEEKS_WORKED)
```


```{r}
qplot(DISABILITY,
      geom="histogram",
      binwidth = 1,  
      main = "Histogram for DISABILITY", 
      xlab = "DISABILITY",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(DISABILITY,
  main = "DISABILITY",
  xlab = "Count",
  ylab = "DISABILITY",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(DISABILITY), 
     main="DISABILITY DISTRIBUTION")
polygon(density(DISABILITY), col="pink", border="blue")


plot(DISABILITY, EARNINGS)

round(mean(DISABILITY), 0)
(mean(DISABILITY))
median(DISABILITY)
round(sqrt(var(DISABILITY, y = NULL)))
(sqrt(var(DISABILITY, y = NULL)))
min(DISABILITY)
max(DISABILITY)
```


```{r}
qplot(RAW_LIMITED$NATIVITY,
      geom="histogram",
      binwidth = 1,  
      main = "Histogram for NATIVITY", 
      xlab = "NATIVITY",  
      fill=I("orange"), 
      col=I("black"), 
      #alpha=I(.5),
      )

boxplot(RAW_LIMITED$NATIVITY,
  main = "NATIVITY",
  xlab = "Count",
  ylab = "NATIVITY",
  col = "darkorchid",
  border = "brown",
  horizontal = TRUE,
  notch = FALSE
)

plot(density(RAW_LIMITED$NATIVITY), 
     main="NATIVITY DISTRIBUTION")
polygon(density(RAW_LIMITED$NATIVITY), col="pink", border="blue")

plot(RAW_LIMITED$NATIVITY, EARNINGS)

round(mean(RAW_LIMITED$NATIVITY), 0)
(mean(RAW_LIMITED$NATIVITY))
median(RAW_LIMITED$NATIVITY)
round(sqrt(var(RAW_LIMITED$NATIVITY, y = NULL)))
(sqrt(var(RAW_LIMITED$NATIVITY, y = NULL)))
min(RAW_LIMITED$NATIVITY)
max(RAW_LIMITED$NATIVITY)
```

```{r}
colnames(NEW_DAT)
```


```{r}
corrplot(cor(cbind(EARNINGS, AGE, SUPP_INC, SOCIAL_SECURITY)))

corrplot(cor(cbind(EARNINGS, AGE, HR_WORKED, WK_WORKED)))

corrplot(cor(cbind(EARNINGS, AGE, PRI_SEC, GOV_SEC, SELF_EMP, WRK_UNPAID)))

corrplot(cor(cbind(EARNINGS, AGE, MULTI)))

corrplot(cor(cbind(EARNINGS, AGE, MARRIED, WIDOWED, DIVORCED, SEPARATED, NOT_MARRIED)))

corrplot(cor(cbind(EARNINGS, AGE, INCOMP_EDU, PRIM_EDU, SEC_INCOMP, SEC_DIP, SEC_EDU, GED_EDU, SOME_SEC)))

corrplot(cor(cbind(EARNINGS, AST_EDU, BACH_EDU, SOME_COL, MAST_EDU, PROF_EDU, DOC_EDU)))

corrplot(cor(cbind(EARNINGS, AGE, MALE, FEMALE, DISABILITY, NATIVITY)))
```

```{r}
cor(NEW_DAT[, c("EARNINGS", "AGE", "SUPP_INC", "SOCIAL_SECURITY")])

cor(NEW_DAT[, c("EARNINGS", "AGE", "HR_WORKED", "WK_WORKED")])

cor(NEW_DAT[, c("EARNINGS", "AGE", "PRI_SEC", "GOV_SEC", "SELF_EMP", "WRK_UNPAID")])

cor(NEW_DAT[, c("EARNINGS", "AGE", "MULTI")])

cor(NEW_DAT[, c("EARNINGS", "AGE", "MARRIED", "WIDOWED", "DIVORCED", "SEPARATED", "NOT_MARRIED")])

cor(NEW_DAT[, c("EARNINGS", "AGE", "INCOMP_EDU", "PRIM_EDU", "SEC_INCOMP", "SEC_DIP", "SEC_EDU", "GED_EDU", "SOME_SEC")])

cor(NEW_DAT[, c("EARNINGS", "AST_EDU", "BACH_EDU", "SOME_COL", "MAST_EDU", "PROF_EDU", "DOC_EDU")])

cor(NEW_DAT[, c("EARNINGS", "AGE", "MALE", "FEMALE", "DISABILITY", "NATIVITY")])
```


```{r}
corrplot(cor(cbind(HR_WORKED, WK_WORKED, PRI_SEC, GOV_SEC, SELF_EMP, WRK_UNPAID)))

corrplot(cor(cbind(HR_WORKED, WK_WORKED, MULTI)))

corrplot(cor(cbind(MULTI, PRI_SEC, GOV_SEC, SELF_EMP, WRK_UNPAID)))

```

```{r}
cor(NEW_DAT[, c("HR_WORKED", "WK_WORKED", "PRI_SEC", "GOV_SEC", "SELF_EMP", "WRK_UNPAID")])

cor(NEW_DAT[, c("HR_WORKED", "WK_WORKED", "MULTI")])

cor(NEW_DAT[, c("MULTI", "PRI_SEC", "GOV_SEC", "SELF_EMP", "WRK_UNPAID")])
```


```{r}
corrplot(cor(cbind(HR_WORKED, WK_WORKED, PRI_SEC, GOV_SEC, SELF_EMP, WRK_UNPAID)))

corrplot(cor(cbind(HR_WORKED, WK_WORKED, MARRIED, WIDOWED, DIVORCED, SEPARATED, NOT_MARRIED)))

corrplot(cor(cbind(PRI_SEC, GOV_SEC, SELF_EMP, WRK_UNPAID, INCOMP_EDU, PRIM_EDU, SEC_INCOMP, SEC_DIP, SEC_EDU, GED_EDU, SOME_SEC)))

corrplot(cor(cbind(PRI_SEC, GOV_SEC, SELF_EMP, WRK_UNPAID, AST_EDU, BACH_EDU, SOME_COL, MAST_EDU, PROF_EDU, DOC_EDU)))

corrplot(cor(cbind(MARRIED, WIDOWED, DIVORCED, SEPARATED, NOT_MARRIED, AST_EDU, BACH_EDU, SOME_COL, MAST_EDU, PROF_EDU, DOC_EDU)))

corrplot(cor(cbind(MARRIED, WIDOWED, DIVORCED, SEPARATED, NOT_MARRIED, AST_EDU, BACH_EDU, SOME_COL, MAST_EDU, PROF_EDU, DOC_EDU)))

```

```{r}
cor(NEW_DAT[, c("HR_WORKED", "WK_WORKED", "PRI_SEC", "GOV_SEC", "SELF_EMP", "WRK_UNPAID")])

cor(NEW_DAT[, c("HR_WORKED", "WK_WORKED", "MARRIED", "WIDOWED", "DIVORCED", "SEPARATED", "NOT_MARRIED")])

cor(NEW_DAT[, c("PRI_SEC", "GOV_SEC", "SELF_EMP", "WRK_UNPAID", "INCOMP_EDU", "PRIM_EDU", "SEC_INCOMP", "SEC_DIP", "SEC_EDU", "GED_EDU", "SOME_SEC")])

cor(NEW_DAT[, c("PRI_SEC", "GOV_SEC", "SELF_EMP", "WRK_UNPAID", "AST_EDU", "BACH_EDU", "SOME_COL", "MAST_EDU", "PROF_EDU", "DOC_EDU")])

cor(NEW_DAT[, c("MARRIED", "WIDOWED", "DIVORCED", "SEPARATED", "NOT_MARRIED", "AST_EDU", "BACH_EDU", "SOME_COL", "MAST_EDU", "PROF_EDU", "DOC_EDU")])

cor(NEW_DAT[, c("MARRIED", "WIDOWED", "DIVORCED", "SEPARATED", "NOT_MARRIED", "AST_EDU", "BACH_EDU", "SOME_COL", "MAST_EDU", "PROF_EDU", "DOC_EDU")])
```


```{r}
corrplot(cor(cbind(MALE, FEMALE, PRI_SEC, GOV_SEC, SELF_EMP, WRK_UNPAID)))

corrplot(cor(cbind(MALE, FEMALE, MARRIED, WIDOWED, DIVORCED, SEPARATED, NOT_MARRIED)))

corrplot(cor(cbind(MALE, FEMALE, PRI_SEC, GOV_SEC, SELF_EMP, WRK_UNPAID)))

corrplot(cor(cbind(MALE, FEMALE, INCOMP_EDU, PRIM_EDU, SEC_INCOMP, SEC_DIP, SEC_EDU, GED_EDU, SOME_SEC)))

```

```{r}
cor(NEW_DAT[, c("MALE", "FEMALE", "PRI_SEC", "GOV_SEC", "SELF_EMP", "WRK_UNPAID")])

cor(NEW_DAT[, c("MALE", "FEMALE", "MARRIED", "WIDOWED", "DIVORCED", "SEPARATED", "NOT_MARRIED")])

cor(NEW_DAT[, c("MALE", "FEMALE", "PRI_SEC", "GOV_SEC", "SELF_EMP", "WRK_UNPAID")])

cor(NEW_DAT[, c("MALE", "FEMALE", "INCOMP_EDU", "PRIM_EDU", "SEC_INCOMP", "SEC_DIP", "SEC_EDU", "GED_EDU", "SOME_SEC")])
```


```{r}
corrplot(cor(cbind(DISABILITY, NATIVITY, PRI_SEC, GOV_SEC, SELF_EMP, WRK_UNPAID)))

corrplot(cor(cbind(DISABILITY, NATIVITY, MARRIED, WIDOWED, DIVORCED, SEPARATED, NOT_MARRIED)))

corrplot(cor(cbind(DISABILITY, NATIVITY, PRI_SEC, GOV_SEC, SELF_EMP, WRK_UNPAID)))

corrplot(cor(cbind(DISABILITY, NATIVITY, INCOMP_EDU, PRIM_EDU, SEC_INCOMP, SEC_DIP, SEC_EDU, GED_EDU, SOME_SEC)))
```

```{r}
cor(NEW_DAT[, c("DISABILITY", "NATIVITY", "PRI_SEC", "GOV_SEC", "SELF_EMP", "WRK_UNPAID")])

cor(NEW_DAT[, c("DISABILITY", "NATIVITY", "MARRIED", "WIDOWED", "DIVORCED", "SEPARATED", "NOT_MARRIED")])

cor(NEW_DAT[, c("DISABILITY", "NATIVITY", "PRI_SEC", "GOV_SEC", "SELF_EMP", "WRK_UNPAID")])

cor(NEW_DAT[, c("DISABILITY", "NATIVITY", "INCOMP_EDU", "PRIM_EDU", "SEC_INCOMP", "SEC_DIP", "SEC_EDU", "GED_EDU", "SOME_SEC")])
```

```{r}
sum(MULTI)
sum(MALE)
sum(FEMALE)
sum(DISABILITY)
```
























